figures and calculations for global fisheries management

### 2019-01-21 documents/figs-and-calcs.Rmd
pre pull

figure_6 <- results %>%
  filter(year == max(year)) %>%
  ggplot() +
  geom_raster(aes(cost, discount, fill = b / (k/2)),
              interpolate = TRUE) +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = c(min(scenes$cost), 750, 1500),
    labels = c("Low", "Medium", "High"),
    name = "Fishing Costs"
  ) +
  stat_contour(breaks=c(1),aes(cost, discount, z = b / (k/2)), color ="black")+
  scale_y_continuous(expand = c(0, 0),
                     name = "Discount Rate",
                     labels = scales::percent) +
  scale_fill_gradient2(
    low = "tomato",
    mid = "white",
    high = "steelblue",
    midpoint = 1,
    name = "Bmey",
    guide = guide_colorbar(frame.colour = "black",
                           barheight = unit(15, "lines")),
    limits = c(0,2)
  ) + 
  theme(panel.border = element_rect(color = "black",
                                    fill = "transparent"))

@@

catch_shares_and_turfs %>% 
  filter(Year == 2012) %>% 
group_by(TURF) %>% 
  summarise(n = length(Catch),
            tc = sum(Catch, na.rm = T))
upjoin <-
  caret::upSample(
    x = select(catch_shares_and_turfs, -TURF),
    y = factor(catch_shares_and_turfs$TURF),
    yname = "TURF"
  )

cs_or_turf_fit <-
  glm(
    formula = TURF ~ gdp + SpeciesCatName + Catch,
    family = "binomial",
    data = catch_shares_and_turfs 
  )

@@

stargazer::stargazer(cs_or_turf_fit,
                     covariate.labels =covar_names,
                     intercept.top = TRUE,
                     intercept.bottom = FALSE)

@@

temp <- projection_turfs %>%
  filter(SpeciesCatName %in% unique(catch_shares_and_turfs$SpeciesCatName),
         Year == 2012) %>% 
  select(-gdp) %>% 
  rename(gdp = gdp_center)

@@

knitr::kable(country_pred_summary, format = "latex", longtable = TRUE)

@@

>>>>

figure_6 <- results %>%
  filter(year == max(year)) %>%
  ggplot() +
  geom_raster(aes(cost, discount, fill = b / (k/2)),
              interpolate = TRUE) +
  scale_x_continuous(
    expand = c(0, 0),
    breaks = c(min(scenes$cost), 750, 1500),
    labels = c("Low", "Medium", "High"),
    name = "Fishing Costs"
  ) +
  stat_contour(breaks=c(1),aes(cost, discount, z = b / (k/2)), color ="black")+
  scale_y_continuous(expand = c(0, 0),
                     name = "Discount Rate",
                     labels = scales::percent) +
  scale_fill_gradient2(
    low = "tomato",
    mid = "white",
    high = "steelblue",
    midpoint = 1,
    name = "B*/Bmsy",
    guide = guide_colorbar(frame.colour = "black",
                           barheight = unit(15, "lines")),
    limits = c(0,2)
  ) + 
  theme(panel.border = element_rect(color = "black",
                                    fill = "transparent"))

@@

catch_shares_and_turfs %>% 
  filter(Year == 2012) %>% 
group_by(TURF) %>% 
  summarise(n = length(Catch),
            tc = sum(Catch, na.rm = T))

catch_shares_and_turfs %>% 
  group_by(MainCat) %>% 
  count()

upjoin <-
  caret::upSample(
    x = select(catch_shares_and_turfs, -TURF),
    y = factor(catch_shares_and_turfs$TURF),
    yname = "TURF"
  )

 fit_recipe <- recipes::recipe( ~ SpeciesCat, data = catch_shares_and_turfs) %>% 
     step_other(SpeciesCat, threshold = .02, other = "other values")

rec <- prep(fit_recipe, training = catch_shares_and_turfs, retain = TRUE)

dat <- juice(rec)
 dat %>% group_by(SpeciesCat) %>% count()

 catch_shares_and_turfs$short_SpeciesCat <- dat$SpeciesCat

cs_or_turf_fit <-
  glm(
    formula = TURF ~ gdp + short_SpeciesCat,
    family = "binomial",
    data = catch_shares_and_turfs 
  )

@@

@@

pROC::auc(pROC::roc(TURF ~ pred, data = orig_cs_or_turf_fit))

spcat_match <- catch_shares_and_turfs %>% 
  select(SpeciesCat, short_SpeciesCat) %>% 
  unique()

temp <- projection_turfs %>%
  left_join(spcat_match, by = "SpeciesCat") %>% 
  filter(!is.na(short_SpeciesCat)) %>% 
  select(-gdp) %>% 
  rename(gdp = gdp_center)

@@

knitr::kable(country_pred_summary, format = "latex", longtable = TRUE, booktabs = TRUE)

@@

summary(cs_or_turf_fit)
```
